{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-26 paper/paper.tex
corrected noninterference defintion
removed todo
beautified def of seq type system

\todo{Explain how the programs are executed}
To define what noninterference means we need a notion of excution. It is assumed
that we have a sequential execution relation $\leadsto_{seq} \subseteq SeqState \times
SeqState$. The one step execution for the multithreaded language $\leadsto_{seq}
\subseteq (ConcState \times History) \times (ConcState \times History)$ is defined
by the following rules.

@@

\begin{align*}
\mu_1 \sim_g \mu_2 \land P,\mu_1 \Downarrow \mu_1' \land P,\mu_2 \Downarrow \mu_2' \rightarrow \mu_1' \sim_g \mu_2'
\end{align*}

@@

\todo{Explain intuition}
\begin{enumerate}
\item We have a partial ordered set $(LType, \leq)$ of local types, with an initial
      type $t_{init}$
\item and typing judgments of the form $se, i \vdash_{seq} s \Rightarrow t$, where
      $s, t \in LType$, $i \in \mathcal{P}$ and se is a securirty environment.
\end{enumerate}

>>>>

To define what noninterference means we need a notion of excution. It is assumed
that we have a sequential execution relation $\leadsto_{seq} \subseteq SeqState \times
SeqState$. The one step execution for the multithreaded language $\leadsto_{seq}
\subseteq (ConcState \times History) \times (ConcState \times History)$ is defined
by the following rules.

@@

\begin{align*}
\mu_1 \sim_g \mu_2 \land P,\mu_1 \Downarrow_{conc} \mu_1' \land P,\mu_2 \Downarrow_{conc} \mu_2' \Rightarrow \mu_1' \sim_g \mu_2'
\end{align*}

@@

\todo{Explain intuition}
\begin{enumerate}
\item We have a partial ordered set $(\text{LType}, \leq)$ of local types, with an initial
      type $t_{init}$
\item and typing judgments of the form $se, i \vdash_{seq} s \Rightarrow t$, where
      $s, t \in \text{LType}$, $i \in \mathcal{P}$ and se is a securirty environment.
\end{enumerate}
